A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-18 papers/execution-model/model.tex
Add files via upload
section 3

\section{Execution Model}
\label{sec:execution-model}

@@

\end{enumerate}
\end{document}

>>>>

\section{Execution Model}
\label{sec:execution-model}
The context of our work is the Tezos blockchain \cite{tezos-whitepaper}\cite{tezos-intropaper}. Tezos is a self-amending blockchain that improves on several aspects compared to more established 
blockchains. Tezos introduces an original consensus algorithm called Liquid Proof of Stake that allows consensus not only on the state of its ledger, like Bitcoin \cite{bitcoin-whitepaper} or Ethereum \cite{eth-whitepaper}, but also on how the economic protocol and the nodes should adapt and upgrade, and serves as a decentralized smart contract platform that facilitates formal verification and focuses on formal methods to improve security.

In Tezos, there are two types of accounts: implicit accounts and smart contracts, and they are stateful. An implicit account is a non-programmable account, whose tokens are spendable and associated with a pair of private/public keys. A smart contract is a programmable account that is created with an origination operation and has no corresponding secret key. The address of a smart contract is a unique public hash that depends on the creation operation. All existing accounts are stored in a context component on the blockchain. An implicit account is managed with its public key, balance, and counter, whose job is to prevent replay attacks. A smart contract account is stored with its script, storage, and balance. Tezos provides the Michelson language for writing a smart contract. Michelson is a stack-based language with strict static type checking. A contract is a function that maps a pair of parameters and a storage that have fixed and monomorphic types to a pair of a list of internal operations and an updated storage. The script of a smart contract must be type-checked before it is introduced into the system.

An implicit account can perform three kinds of transactions: (1) transfer tokens to another implicit account, (2) transfer (invoke) a smart contract, or (3) originate a smart contract to create a new smart contract on the blockchain. An origination transaction specifies the script of the contract and the initial content of the storage of the contract. A smart contract invocation provides input data. Each transaction usually includes a fee that is for either by paying to a baker or by destroying (burning). A transaction can only be sent if it has been signed with the sender contract's private key and it is injected into the blockchain network via a node that runs Gossip network and updates the context. The node first validates the transaction before submitting it to the network. In general, a transaction can fail for a number of reasons,  including an incorrect recipient address, insufficient balance, an incorrect counter, and an incorrect type of input parameter(or script). A transaction is valid only if the counter of the sender contract is equal to the counter that is used in the transaction. A smart contract invocation may fail for reasons determined by the contract's script. An invalid transaction is rejected by the node.

Once the transaction is valid, it is injected into the mempool, which contains all pending transactions before they can be included in a block. These transactions are then broadcasted to the network. On the other hand, a pending transaction may get lost in the mempool. Namely, it may be dropped. There are several
causes for dropping, primarily timeout or overflow of the mempool, which is limited in size in the implementation. A transaction times out when 60 blocks have passed and it no longer be included anymore in a block. When a transaction is included in a blockchain, the amount of tokens transferred is added to the balance of destination contract and when a smart contract call is made, the script of the destination contract is executed. %This script uses the parameters passed to it, reads the contract's storage and then executes its intructions. 
Once a transaction is applied, the counter increments by one, preventing the transaction from being reused.

@@

\end{enumerate}

\bibliographystyle{splncs04}
\bibliography{bio}
\end{document}
